---
title: "R Notebook"
output: html_notebook
---

## HEADLINE 

## Libraries
Loading all the necessary libraries!

```{r}
library(dplyr)
library(tidyverse)
library(stringr)


library(usethis)
use_git_config(user.name = "malina-a", user.email = "malina.aniol@sciencespo.fr")

```


use "data/EES_aggregated_macrovariables.dta", clear

```{r}
load("C:/Users/malin/Downloads/EES_aggregated_macrovariables.RData")
a <- table
```

add macro-level variables
```{r}

a$presidential <- 0

a$presidential[a$country == 1 |a$country == 3 |a$country == 4|a$country == 10|a$country == 14|a$country == 17|a$country == 21|a$country == 22|a$country == 23] <- 1

a$presidential[a$country==6 & a$year>=2013] <- 1
a$presidential[a$country==24 & a$year>=1999] <- 1
a$presidential[a$country==25 & a$year<=2002] <- 1
a$presidential[a$country==25 & a$year>=2012] <- 1

# alternative dplyr version

# table <- table %>%
#   mutate(presidential = case_when(
#     country %in% c(1, 3, 4, 10, 14, 17, 21, 22, 23) ~ 1,
#     country == 6 & year >= 2013 ~ 1,
#     country == 24 & year >= 1999 ~ 1,
#     country == 25 & year <= 2002 ~ 1,
#     country == 25 & year >= 2012 ~ 1,
#     TRUE ~ 0  # default value
#   ))


a <- a |>
  mutate(legislative_type = case_when(
    country %in% c(3,4,11,19,12,13,15,17,23) ~ 1,
    country == 10 ~ 2,
    country == 28 ~2,
    country==3 & year==2009 ~ 2,
    country==4 & year<=1995 ~ 2,
    country==15 & year>=1994 & year <=2001 ~ 2,
    country==23 & year>=2008 & year<=2012 ~ 2,
    TRUE ~ 0
  ))

a <- a |>
  mutate(majoritarian = case_when(
    legislative_type ==1 ~ 0,
    legislative_type==2 ~ 1
  ))
  

```

** add math score data

```{r}

load("D:/Rep_R/Rep_Kostelka/maths_diff_to_merge.RData")
m <- table


a$countryyear <- paste(a$country,a$year, sep = "") # alternatively paste0

mmaths <- merge(a,m, by =c("country","year", "countryyear"))

```


add EIGE data
** add gender equality index data 
	merge m:1 country year using "data/EIGE_to_merge1.dta" 
	drop _merge	EIGE_country long_term_index

	merge m:1 country using "data/EIGE_to_merge2.dta"
	drop _merge	
	
	lab var value "EIGE" 
	lab var long_term_index "EIGE (2005-2015 average)" 
```{r}

load("D:/Rep_R/REP_Kostelka_GenderGap/EIGE_to_merge1.RData")
eige1 <- table

load("D:/Rep_R/REP_Kostelka_GenderGap/EIGE_to_merge2.RData")
eige2 <- table

me1 <- merge(mmaths, eige1, by = c("country", "year"), all.x = TRUE)

mee <- merge(me1, eige2, by = "country", all.x =TRUE)

mee <- mee |>
  select(-EIGE_country.x, -long_term_index.x, -EIGE_country.y, -long_term_index.y)


```


** add EVS survey data 
	merge m:1 country using "data/EVS_to_merge.dta"
	drop _merge	
	
```{r}
load("D:/Rep_R/REP_Kostelka_GenderGap/EVS_to_merge.RData")

evs <- table

meeevs1 <- merge (mee, evs, by = "country", all.x = TRUE, all.y = FALSE)

```


* Generating filter with missing values on some of the individual IVs
	
	gen filter=1
	replace filter=0 if mi(female, age, postsecondary, social_class, employment_status, interest, close_to_party, tu_member, religiosity, membership_good)
	
	sum female age postsecondary social_class employment_status interest close_to_party tu_member religiosity membership_good
	sum female age postsecondary social_class employment_status interest close_to_party tu_member religiosity membership_good if filter==1
	
	gen filter2=1
	replace filter2=0 if mi(female, age, postsecondary, social_class, employment_status, interest, close_to_party)
	
```{r}
meeevs$filter1 <- 1

meeevs$filter1[is.na(meeevs$female)| is.na(meeevs$age)| is.na(meeevs$postsecondary)| is.na(meeevs$social_class)| is.na(meeevs$employment_status)| is.na(meeevs$interest)| is.na(meeevs$close_to_party)| is.na(meeevs$tu_member)| is.na(meeevs$religiosity)| is.na(meeevs$membership_good)] <- 0

meeevs$filter2 <- 1

meeevs$filter2[is.na(meeevs$female)| is.na(meeevs$age)| is.na(meeevs$postsecondary)| is.na(meeevs$social_class)| is.na(meeevs$employment_status)| is.na(meeevs$interest)| is.na(meeevs$close_to_party)] <- 0


```



	
********************
**	MAIN RESULTS  **
********************


* Figure 1. evolution of the gender gap in turnout

	cap set scheme bw

	recode country (2 7 10 14 11 15 18 20 28=1 "Member States in 1979") (else=0), gen(ms1979)

	eststo clear
	foreach k of numlist 1979 1984 1989 1994 1999 2004 2009 2014 {
	reg vote_eur i.female i.country if year==`k', l(90)
	eststo M_`k'_graph_all: margins, dydx(female) post
	}

	foreach k of numlist 1979 1984 1989 1994 1999 2004 2009 2014 {
	reg vote_eur i.female i.country if year==`k' & ms1979==1, l(90)
	eststo M_`k'_graph_MS1979: margins, dydx(female) post
	}

	coefplot (M_1979_graph_all, label("All Member States") msymbol(Oh)) (M_1979_graph_MS1979, label("1979 Member States") msymbol(O)), bylabel(1979) || ///
	M_1984_graph_all M_1984_graph_MS1979, bylabel(1984) || M_1989_graph_all M_1989_graph_MS1979, bylabel(1989) || /// 
	M_1994_graph_all M_1994_graph_MS1979, bylabel(1994) || M_1999_graph_all M_1999_graph_MS1979, bylabel(1999) || /// 
	M_2004_graph_all M_2004_graph_MS1979, bylabel(2004) || M_2009_graph_all M_2009_graph_MS1979, bylabel(2009) || /// 
	M_2014_graph_all M_2014_graph_MS1979, bylabel(2014) bycoef vertical ytitle("Gender gap in the probability to vote", size(medsmall) height(-3)) ///  
	legend(size(small) bm(medsmall)) ylabel(, labs(small))  xlabel(, labs(small)) yline(0, lp(dash))

	graph export "Figure1.eps", replace
